\documentclass{article}
% Uncomment the line below after adding neurips_2023.sty to this folder
% \usepackage[preprint]{neurips_2023}

\usepackage[utf8]{inputenc}
\usepackage[T1]{fontenc}
\usepackage{hyperref}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{amsmath, amssymb}

\title{Retail Customer Purchase Prediction}

\author{%
  Benjamin Tran \and Matthew Nguyen \and Victor Bui \and Gustavo Buenrostro\\
  University of Houston\\
  \texttt{\{emails\}@uh.edu}
}

\begin{document}
\maketitle

\begin{abstract}
Briefly describe the problem, approach, and key results (<= 300 words). Primary metric: ROC-AUC; compare LR, DT/RF/(Boosting), and MLP.
\end{abstract}

\section{Introduction}
Problem motivation, why it matters, and summary of contributions. Outline of the paper.
% Talk about purchase intent prediction, supervised learning framing, business relevance.

\section{Background / Related Work}
Prior work on purchase intent prediction, classical ML vs shallow NNs on tabular data, evaluation metrics. Cite datasets/papers.

\section{Data}
Describe UCI Online Shoppers dataset (features, label, imbalance), preprocessing (one-hot, scaling), and split (train/val/test). If used, describe aggregation for Online Retail II (RFM). Leakage audit.

\section{Methods}
Models: Logistic Regression (baseline), Decision Tree, Random Forest, (optional) Gradient Boosting, MLP (architecture, regularization, early stopping). Class imbalance handling. Justify choices.

\section{Experiments}
Validation setup, hyperparameters (brief), metrics (ROC-AUC primary; F1/Precision/Recall). Figures: ROC curves, confusion matrices, feature importance (trees), learning curve (MLP). Ablations: feature groups, model families.

\section{Results \& Discussion}
Report main numbers on validation/test; discuss trade-offs (interpretability vs performance). Business takeaways: what signals most influence conversion.

\section{Conclusion}
Key findings, limitations, and future work (e.g., calibration, cost-sensitive thresholds, deployment thoughts).

\bibliographystyle{plain}
\bibliography{references}
\end{document}
